Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-01 paper/experiments.tex
First draft

\begin{figure*}[htbp]
    \vskip 0.2in
    \begin{center}
        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions}
        \label{fig:CovPlotBenchmark}
    \end{center}
    \vskip -0.2in
\end{figure*}

@@

\textcolor{red}{TODO: qKG and qEI}

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

@@

\textcolor{red}{TODO: qKG and qEI}

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
\caption{Optimization results of the class-E power amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

>>>>

@@

%TODO: Introduce the importance of OpAmp and PA

\begin{figure}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
        \caption{Schematic of the operational amplifier}
        \label{fig:schDAC2014}
    \end{center}
\end{figure}

The operational amplifier~\cite{wang2014enabling} shown in Figure~\ref{fig:schDAC2014} is used for
comparison, the circuit is designed using the 180nm process. It has ten design
parameters, including the lengths and widths of transistors, the resistance of
resistors and the capacitance of capacitors. The circuit is simulated using the
HSPICE circuit simulator.

We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the $FOM$ is constructed as:
$$
\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
$$

For this circuit, we compared the MACE algorithm with the BLCB and EI-LP
algorithms, the qKG and qEI are not compared as the calculation of qEI and qKG
acquisition functions become very slow for the ten dimensionl functions.

We run the algorithms in sequential mode and batched mode, for the batched
mode, batch size is set to $B = 4$. The number initial random sampling is set
to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{fig:resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

The mean convergence plot for the sequential and batched runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared to other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared to the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.

@@

\begin{figure}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.png}}
        \caption{Schematic of the power amplifier\textcolor{red}{TODO: replace this schematic with eps file} }
        \label{fig:schPA}
    \end{center}
\end{figure}

The power amplifier shown in Figure~\ref{fig:schPA} is used for comparison, the
circuit is designed using the 180nm process with twelve design parameters, the
circuit is simulated by HSPICE to get its performances.

For this power amplifier, we aim to maximize the power added effiency (PAE) and the output power (Pout), the $FOM$ is constructed as
$$
\mathit{FOM} = -3 * \mathit{PAE} - \mathit{Pout}
$$

The MACE, BLCB and EI-LP algorithms were tested in both, sequential and batched
mode, the number of initial sampling is $N_{init} = 100$, the number of
iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
number of HSPICE simulations is 500 for each batched run and 200 for each
sequential run.

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
\caption{Optimization results of the class-E power amplifier}
\label{fig:resClassE}
\end{center}
\vskip -0.2in
\end{figure}

\begin{figure*}[]
    \begin{center}
        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
        \caption{Optimization results of the benchmark functions}
        \label{fig:CovPlotBenchmark}
    \end{center}
\end{figure*}

The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
that the MACE outperformed the BLCB and EI-LP in both sequential and batched
mode. For the batched runs, the MACE convergences fastest among the three
algorithms, while the sequential MACE has similar performance as the batched
EI-LP method.
